The Correspondence Analysis of Two Mode Networks Revisited

### 2025-03-30 analysis-R1.qmd
do it

@@

```{r Bonacich Similarity and Correspondence Plot}
      norm.sim.r <- A %*% t(A)
      norm.sim.c <- t(A) %*% A
      diag(norm.sim.r) <- 0
      diag(norm.sim.c) <- 0
      norm.sim.r <- norm.sim.r[order(eig.r[, 1]), order(eig.r[ ,1])]
      norm.sim.c <- norm.sim.c[order(eig.c[, 1]), order(eig.c[ ,1])]
      # Bonacich Similarity Plot (People)
      p <- ggcorrplot(norm.sim.r)
      p <- p + scale_x_discrete(position = "top")
      p <- p + scale_y_discrete(limits = rev)
      p <- p + scale_fill_gradient2(limit = c(0, max(norm.sim.r+1)), 
                                    low = "white", 
                                    high =  "darkred", 
                                    mid = "red",  
                                    midpoint = max(norm.sim.r)/2)
      a <- p + theme(legend.position = "none",
                    axis.text.x = element_text(hjust = -0.2, size = 10))

      # Bonacich Similarity Plot (Groups)
      p <- ggcorrplot(norm.sim.c)
      p <- p + scale_x_discrete(position = "top")
      p <- p + scale_y_discrete(limits = rev)
      p <- p + scale_fill_gradient2(limit = c(0, max(norm.sim.c+1)), 
                                    low = "white", 
                                    high =  "darkred", 
                                    mid = "red",  
                                    midpoint = max(norm.sim.c)/2)
      b <- p + theme(legend.position = "none", plot.margin = margin(l = 100),
                    axis.text.x = element_text(hjust = -0.2, size = 10))

      # K-means clustering of Bonacich solution
      eig.dat <- data.frame(d1 = eig.d1, d2 = eig.d2)
      eig.clus.p <- kmeans(eig.dat[1:18,], centers = 3, nstart = 25)$cluster
      eig.clus.g <- kmeans(eig.dat[19:32,], centers = 3, nstart = 25)$cluster

      # Bonacich Correspondence Plot
      eig.d1 <- c(eig.r[, 1], eig.c[, 1])*-1
      eig.d2 <- c(eig.r[, 2], eig.c[, 2])*-1
      plot.dat <- data.frame(eig.d1, eig.d2, 
                             mode = c(rep(1, 18), rep(2, 14)),
                             clus = c(eig.clus.p, eig.clus.g+3)
                             )
      p <- ggplot(plot.dat, aes(y = eig.d2, x = eig.d1, color = factor(clus), 
                                label = c(rownames(A), colnames(A))))
      p <- p + geom_vline(xintercept = 0, color = "gray")
      p <- p + geom_hline(yintercept = 0, color = "gray")
      p <- p + geom_text_repel(size = 4, max.overlaps = 50, fontface = "bold")
      p <- p + theme_minimal() 
      p <- p + theme(legend.position = "none",
                     axis.text = element_text(size = 18),
                     axis.title = element_text(size = 20)
                     )
      c <- p + labs(x = "First Dimension", y = "Second Dimension")
      #c <- p + scale_color_manual(values = c('red', 'blue'))
      png(file = here("Plots", "bon-corr-plot.png"), width=1500, height=1000)
      (a + b) / (c) + 
         plot_annotation(tag_levels = 'a', tag_suffix = ')') & 
         theme(plot.tag = element_text(size = 26))
      dev.off()
```

>>>>

```{r Correlation between odds and even reflections and Bonacich Score}
   a <- reflections(A, iter = 42)
   p.e.r <- a$p.r[, evens(1:40)]
   g.e.r <- a$g.r[, evens(1:40)]
   p.o.r <- a$p.r[, odds(3:41)]
   g.o.r <- a$g.r[, odds(3:41)]
   plot.dat.p <- data.frame(p.o = as.vector(abs(cor(eig.r[, 1], p.o.r))),
                            p.e = as.vector(abs(cor(eig.r[, 1], p.e.r))),
                            ref.o = seq(3, 41, by = 2),
                            ref.e = seq(2, 40, by = 2)
                            )
   p <- ggplot(plot.dat.p, aes(x = ref.e, y = p.e))
   p <- p + geom_point(size = 2) + geom_line()
   p <- p + ylim(0, 1) + labs(x = "Even Reflection", y = "Bonacich Correlation")
   p1 <- p + scale_x_continuous(breaks = seq(2, 40, by = 4))
   p <- ggplot(plot.dat.p, aes(x = ref.o, y = p.o))
   p <- p + geom_point(size = 2) + geom_line()
   p <- p + ylim(0, 1) + labs(x = "Odd Reflection", y = "Bonacich Correlation")
   p2 <- p + scale_x_continuous(breaks = seq(3, 41, by = 4))
   png(file = here("Plots", "bon-ref-corr-p.png"), width=800, height=400)
      p1 + p2 & theme_minimal()
   dev.off()
   plot.dat.g <- data.frame(p.o = as.vector(abs(cor(eig.c[, 1], g.o.r))),
                            p.e = as.vector(abs(cor(eig.c[, 1], g.e.r))),
                            ref.o = seq(3, 41, by = 2),
                            ref.e = seq(2, 40, by = 2)
                            )
   p <- ggplot(plot.dat.g, aes(x = ref.e, y = p.e))
   p <- p + geom_point(size = 2) + geom_line()
   p <- p + ylim(0, 1) + labs(x = "Even Reflection", y = "Bonacich Correlation")
   p1 <- p + scale_x_continuous(breaks = seq(2, 40, by = 4))
   p <- ggplot(plot.dat.g, aes(x = ref.o, y = p.o))
   p <- p + geom_point(size = 2) + geom_line()
   p <- p + ylim(0, 1) + labs(x = "Odd Reflection", y = "Bonacich Correlation")
   p2 <- p + scale_x_continuous(breaks = seq(3, 41, by = 4))
   png(file = here("Plots", "bon-ref-corr-g.png"), width=800, height=400)
      p1 + p2 & theme_minimal()
   dev.off()
```

@@

```{r Bonacich Similarity and Correspondence Plot}
      sim.p <- A %*% t(A)
      sim.g <- t(A) %*% A
      diag(norm.sim.r) <- 0
      diag(norm.sim.c) <- 0
      sim.p <- sim.p[order(eig.r[, 1]), order(eig.r[ ,1])]
      sim.g <- sim.g[order(eig.c[, 1]), order(eig.c[ ,1])]
      # Bonacich Similarity Plot (People)
      p <- ggcorrplot(sim.p)
      p <- p + scale_x_discrete(position = "top")
      p <- p + scale_y_discrete(limits = rev)
      p <- p + scale_fill_gradient2(limit = c(0, max(sim.p+1)), 
                                    low = "white", 
                                    high =  "darkred", 
                                    mid = "red",  
                                    midpoint = max(sim.p)/2)
      a <- p + theme(legend.position = "none",
                    axis.text.x = element_text(hjust = -0.2, size = 10))

      # Bonacich Similarity Plot (Groups)
      p <- ggcorrplot(sim.g)
      p <- p + scale_x_discrete(position = "top")
      p <- p + scale_y_discrete(limits = rev)
      p <- p + scale_fill_gradient2(limit = c(0, max(sim.g+1)), 
                                    low = "white", 
                                    high =  "darkred", 
                                    mid = "red",  
                                    midpoint = max(sim.g)/2)
      b <- p + theme(legend.position = "none", plot.margin = margin(l = 100),
                    axis.text.x = element_text(hjust = -0.2, size = 10))

      # K-means clustering of Bonacich solution
      eig.dat <- data.frame(d1 = c(eig.r[, 1], eig.c[, 1]), 
                            d2 = c(eig.r[, 2], eig.c[, 2]))
      eig.clus.p <- kmeans(eig.dat[1:18,], centers = 3, nstart = 25)$cluster
      eig.clus.g <- kmeans(eig.dat[19:32,], centers = 3, nstart = 25)$cluster

      # Bonacich Correspondence Plot
      plot.dat <- data.frame(cbind(eig.dat), 
                             mode = c(rep(1, 18), rep(2, 14)),
                             clus = c(eig.clus.p, eig.clus.g+3)
                             )
      p <- ggplot(plot.dat, aes(y = d2, x = d1*-1, 
                                color = factor(clus), 
                                label = c(rownames(A), colnames(A))))
      p <- p + geom_vline(xintercept = 0, color = "gray")
      p <- p + geom_hline(yintercept = 0, color = "gray")
      p <- p + geom_text_repel(size = 4, max.overlaps = 50, fontface = "bold")
      p <- p + theme_minimal() 
      p <- p + theme(legend.position = "none",
                     axis.text = element_text(size = 18),
                     axis.title = element_text(size = 20)
                     )
      c <- p + labs(x = "First Dimension", y = "Second Dimension")
      #c <- p + scale_color_manual(values = c('red', 'blue'))
      png(file = here("Plots", "bon-corr-plot.png"), width=1500, height=1000)
      (a + b) / (c) + 
         plot_annotation(tag_levels = 'a', tag_suffix = ')') & 
         theme(plot.tag = element_text(size = 26))
      dev.off()
```
